Arrows for Parallel Computation

### 2018-01-06 paper/content/main.tex
removed trailing s from paper name
letterspacing in title and other minor thingies

\title{Arrows for Parallel Computations}
\ifthenelse{\boolean{anonymous}}{%
\author{Submission ID xxxxxx}
}{%
%\author{Martin Braun, Phil Trinder, and Oleg Lobachev}
%\affiliation{University Bayreuth, Germany and Glasgow University, UK}
 \author[M. Braun, O. Lobachev and P. Trinder]%
        {MARTIN BRAUN\\
         University Bayreuth, 95440 Bayreuth, Germany\\
		 OLEG LOBACHEV\\
		 University Bayreuth, 95440 Bayreuth, Germany\\
		 \and\ PHIL TRINDER\\
		 Glasgow University, Glasgow, G12 8QQ, Scotland}
}% end ifthenelse

@@

	\end{flushright}\section{Background}
	\label{sec:background}
	\input{arrows}
	\input{parallelHaskells}
	%\pagebreak
	%\pagebreak
	%\pagebreak
	\input{parrows}
	%\pagebreak
	\input{basicSkeletons}
	%\pagebreak
	\input{syntacticSugar}
	%\pagebreak
	\input{futures}
	%\pagebreak
	\input{mapSkeletons}
	%\pagebreak
	\input{topologySkeletons}
	%\pagebreak
	\input{benchmarks}
	%%\pagebreak
	\input{conclusion}
	%\pagebreak
        \bibliographystyle{jfp}
	\bibliography{references,main}
        \appendix
	\input{utilityFunctions}
\end{document}

>>>>

\title{Arrows for Parallel Computation}
\ifthenelse{\boolean{anonymous}}{%
\author{Submission ID xxxxxx}
}{%
%\author{Martin Braun, Phil Trinder, and Oleg Lobachev}
%\affiliation{University Bayreuth, Germany and Glasgow University, UK}
 \author[M. Braun, O. Lobachev, and P. Trinder]%
        {\textls*{MARTIN BRAUN}\\
         University Bayreuth, 95440 Bayreuth, Germany\\
		 \textls*{OLEG LOBACHEV}\\
		 University Bayreuth, 95440 Bayreuth, Germany\\
		 \and\ \textls*{PHIL TRINDER}\\
		 Glasgow University, Glasgow, G12 8QQ, Scotland}
}% end ifthenelse

@@

	\end{flushright}\section{Background}
	\label{sec:background}
	As a introduction, we here give a short overview over Arrows and GpH, the |Par| Monad, and Eden, the three parallel Haskells which we base our DSL on.
	\input{arrows}
	\input{parallelHaskells}
	%\pagebreak
	%\pagebreak
	%\pagebreak
	\input{parrows}
	%\pagebreak
	\input{basicSkeletons}
	%\pagebreak
	\input{syntacticSugar}
	%\pagebreak
	\input{futures}
	%\pagebreak
	\input{mapSkeletons}
	%\pagebreak
	\input{topologySkeletons}
	%\pagebreak
	\input{benchmarks}
	%%\pagebreak
	\input{conclusion}
	%\pagebreak
        \bibliographystyle{jfp}
	\bibliography{references,main}
        \appendix
	\input{utilityFunctions}
\end{document}
